{\LARGE Model Selection for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-01 Paper/main.tex
merge

	\subsection{Hilbert Space of Square-Integrable Functions}
	In functional data analysis, one Hilbert space of particular importance is the space of square-integrable functions on $[0,1]$ denoted $\mathbb{L}^2[0,1]$. To define it, look first at the measure space given by $([0,1], \mathcal{B}, \mu)$ where $\mathcal{B}$ is the Borel $\sigma$-algebra on $[0,1]$ and $\mu$ is the Lebesgue-measure. Then $\mathbb{L}^2[0,1]$ is the collection of all measurable functions $f$ on $[0,1]$ that fulfill the following condition.

	\begin{equation}
		\lvert \lvert f \rvert \rvert^2 = \int_{0}^{1} \lvert f \rvert^2 \mathrm{d}\mu < \infty
	\end{equation}

	All functions $f$ satisfying the above condition are called square-integrable functions. Moreover, it ensures that a random function has a finite second moment so that the variance and the covariance function can be defined. Its inner product is defined as

@@

	$\mathbb{L}^2[0,1]$ is the function space that is most often used for theoretical considerations in functional data analysis without loss of generality. We also focus on the interval [0,1] for the purpose of this paper.	The random function defined on $\mathbb{L}^2[0,1]$ can be represented as

@@

@@

	\begin{equation}
		x(t) = \sum_{i \in \mathcal{I}} c_i(t -w)^{i}
	\end{equation}
	can be expressed as a finite linear combination of the monomials $(t - w)^{i}$ with coefficient $c_i$ which form the basis

@@

		A model in the form of Equation \ref{simplified_model_basis_equation} lends itself to be estimated using theory from multivariate linear regression. Define therefore the following objects

	\begin{equation}
		Y = \begin{pmatrix}
			y_1 \\ \vdots \\ y_n
		\end{pmatrix}, \quad
		Z = \begin{pmatrix}
			1 & \tilde{Z}_{1,1} & \dots & \tilde{Z}_{1,J} \\
			\vdots & \vdots & \ddots & \vdots \\
			1 & \tilde{Z}_{n,1} & \dots & \tilde{Z}_{n,J}
		\end{pmatrix}
	\end{equation}

	Then an OLS estimator can be calculated in the usual way to obtain an estimate for the values of $\alpha$ and $b_j$ and an estimate of the coefficient function can be derived accordingly.

	\begin{equation}
		b^L = \left(Z'Z\right)^{-1}Z'Y \in \mathbb{R}^{L+1} \quad \hat{\alpha} = b_{1}^{L} \quad \hat{\beta}^L(t) = \sum_{j = 1}^{J} b_{j+1}^L \phi_j(t)
	\end{equation}

@@

	As in the previous section, this equation again lends itself for estimation with OLS. Define the following objects:

	\begin{equation}
		Y = \begin{pmatrix}
			y_1 \\ \vdots \\ y_n
		\end{pmatrix}, \quad
		Z = \begin{pmatrix}
			1 & \tilde{\xi}^{1,L}_{1} & \dots & \tilde{\xi}^{M,L}_{1} \\
			\vdots & \vdots & \ddots & \vdots \\
			1 & \tilde{\xi}^{1,L}_{n} & \dots & \tilde{\xi}^{M,L}_{n}
		\end{pmatrix}
	\end{equation}

	We can then derive the following estimators.

	\begin{equation}
		\tilde{b}^{L,M} = \left(Z'Z\right)^{-1}Z'Y \in \mathbb{R}^{M+1} \quad \hat{\tilde{\alpha}} = \tilde{b}_{1}^{L,M} \quad \hat{\tilde{\beta}}^{m,L} = \tilde{b}^{L,M}_{m+1}
	\end{equation}

>>>>

	\subsection{Hilbert Space of Square-Integrable Functions}
	In functional data analysis, one Hilbert space of particular importance is the space of square-integrable functions on $[0,1]$ denoted $\mathbb{L}^2[0,1]$. To define it, look first at the measure space given by $([0,1], \mathcal{B}, \mu)$ where $\mathcal{B}$ is the Borel $\sigma$-algebra on $[0,1]$ and $\mu$ is the Lebesgue-measure.\\
	Then $\mathbb{L}^2[0,1]$ is the collection of all measurable functions $f$ on $[0,1]$ that fulfill the following condition.

	\begin{equation}
		{\color{orange} \lvert \lvert f \rvert \rvert^2 =} \int_{0}^{1} \lvert f \rvert^2 \mathrm{d}\mu < \infty
	\end{equation}

	All functions $f$ satisfying the above condition are called square-integrable functions. Moreover, it ensures that a random function has a finite second moment so that the variance and the covariance function can be defined.\\
	Its inner product is defined as

@@

	The Hilbert space of square integrable functions on $[0,1]$ {\color{orange} (instead, $\mathbb{L}^2[0,1]$)} is the function space that is most often used for theoretical considerations in functional data analysis  {\color{orange} without loss of generality}.

@@

	The random function defined on $\mathbb{L}^2[0,1]$ can be represented as

@@

	\begin{equation}
		x(t) = \sum_{i = 0, i \in \mathcal{I}} c_i(t -w)^{i}
	\end{equation}
	can be expressed as a finite linear combination of the monomials $(t - w)^{i}$ with coefficient $c_i$ which form the basis

@@

	A model in the form of Equation \ref{simplified_model_basis_equation} lends itself to be estimated using theory from multivariate linear regression.

@@
